---
Title: R BASIC CASE STUDY 2 (Credit card)
Author: PARAS BHATTARAI
Date: 30/12/2020
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
``` {r}
require(dplyr)
require(lubridate)
require(ggplot2)
```
####  BUSINESS PROBLEM: 
#### In order to effectively produce quality decisions in the modern credit card 
#### industry, knowledge must be gained through effective data analysis and 
#### modeling. Through the use of dynamic data-driven decision-making tools and 
#### procedures, information can be gathered to successfully evaluate all aspects of 
#### credit card operations. 
#### PSPD Bank has banking operations in more than 50 countries across the globe. 
#### Mr. Jim Watson, CEO, wants to evaluate areas of bankruptcy, fraud, and 
#### collections, respond to customer requests for help with proactive offers and 
#### service.


#### DATA AVAILABLE - 

#### This book has the following sheets: 
#### Customer Acquisition: At the time of card issuing, company maintains 
#### the details of customers. 
#### Spend (Transaction data): Credit card spend for each customer 
#### Repayment: Credit card Payment done by customer 
#### Following are some of Watson's questions to a Consultant (like you) to 
#### understand the customers spend & repayment behavior. 


#### 1. In the above dataset, 
#### a. Incase age is less than 18, replace it with mean of age values. 
#### b. Incase spend amount is more than the limit, replace it with 50% of that 
####  customer's limit. (customer's limit provided in acquisition table is the per 
####  transaction limit on his card) 

```{r} 
Customer_Acqusition <- read.csv("Customer Acqusition.csv")

spend <- read.csv("spend.csv")
 
Repayment <- read.csv("Repayment.csv")


head(Customer_Acqusition)



head(spend)



head(Repayment)
```

##### There is an empty column in the Payment Data
##### Remove empty data from the column 

``` {r}
Repayment$X <- NULL
```

##### Check for NA Value

``` {r}
sum(is.na(Customer_Acqusition))

sum(is.na(spend))

sum(is.na(Repayment))

summary(Repayment)
```
#### 1. In the above dataset,

#### a. Incase age is less than 18, replace it with mean of age valuE


``` {r}
Age <- ifelse(Customer_Acqusition$Age <18, round(mean(Customer_Acqusition$Age, na.rm = TRUE),0), Customer_Acqusition$Age )

Customer_Acqusition$Age <- Age
Customer_Acqusition$Age
```

##### All the customers with age less than 18 have been replaced by mean of the age.


#### b. Incase spend amount is more than the limit, replace it with 50% of that 

```{r}
CUSTOMER_SPENT <- dplyr::left_join(Customer_Acqusition, spend, by = "Customer")  

sum(is.na(CUSTOMER_SPENT))

Amount <- ifelse(CUSTOMER_SPENT$Amount > CUSTOMER_SPENT$Limit, CUSTOMER_SPENT$Limit*0.50, CUSTOMER_SPENT$Amount  )

CUSTOMER_SPENT$Amount <- Amount
CUSTOMER_SPENT$Amount
```
#### c. Incase the repayment amount is more than the limit, replace the repayment with the limit

```{r}
CUSTOMER_Repayment <- dplyr::left_join(Customer_Acqusition, Repayment, by = "Customer")  

sum(is.na(CUSTOMER_Repayment))
```

#### NA IS PRESENT IN USELESS COLUMN. THUS THERE IS NO NEED TO REMOVE THAT

```{r}
Amount <- ifelse(CUSTOMER_Repayment$Amount > CUSTOMER_Repayment$Limit, CUSTOMER_Repayment$Limit, CUSTOMER_Repayment$Amount)

CUSTOMER_Repayment$Amount <- Amount
CUSTOMER_Repayment$Amount
```

#### 2. From the above dataset create the following summaries: 


####   a. How many distinct customers exist? 
  
```{r}
DISTINCT_CUSTOMER <- dplyr::distinct(Customer_Acqusition, Customer)
DISTINCT_CUSTOMER

  length(DISTINCT_CUSTOMER$Customer)

```

#### b. How many distinct categories exist? 
  
  ```{r}
  
  Distinct_Categories <- Customer_Acqusition %>% dplyr::group_by(Segment) %>% dplyr::summarise(Co_uNT = n() )
  Distinct_Categories
```



####  c. What is the average monthly spend by customers? 
  
###### CUSTOMER SPENT DATA WILL BE USED HERE 
  
  ```{r}

CUSTOMER_SPENT$Month <-  lubridate::dmy(CUSTOMER_SPENT$Month)


CUSTOMER_SPENT$YEAR <- lubridate::year(CUSTOMER_SPENT$Month)

CUSTOMER_SPENT$MON_TH <- lubridate::month(CUSTOMER_SPENT$Month, label = TRUE)

Average_monthly_Spent <- CUSTOMER_SPENT %>% dplyr::group_by(YEAR,MON_TH) %>% dplyr::summarise(Average_Monthly_Spent = mean(Amount))

Average_monthly_Spent

```  
  
  
  
####  d. What is the average monthly repayment by customers?


#### CUSTOMER  SPENT DATA WILL BE USED HERE 



```{r}
CUSTOMER_Repayment$Month <-  lubridate::dmy(CUSTOMER_Repayment$Month)

CUSTOMER_Repayment$YEAR <- lubridate::year(CUSTOMER_Repayment$Month)

CUSTOMER_Repayment$MON_TH <- lubridate::month(CUSTOMER_Repayment$Month, label = TRUE)

Average_monthly_Repayment <- CUSTOMER_Repayment %>% dplyr::group_by(YEAR,MON_TH) %>% dplyr::summarise(Average_Monthly_Repayment =mean(Amount))

Average_monthly_Repayment

```



####  e. If the monthly rate of interest is 2.9%, what is the profit for the bank for 
#### each month? (Profit is defined as interest earned on Monthly Profit. 


             ####  Monthly Profit = Monthly repayment – Monthly spend. Interest is 
             ####  earned only on positive profits and not on negative amounts) 



```{r}

monthly_Spent <- CUSTOMER_SPENT %>% dplyr::group_by(YEAR,MON_TH) %>% dplyr::summarise(Average_Monthly = sum(Amount))

monthly_Repayment <- CUSTOMER_Repayment %>% dplyr::group_by(YEAR,MON_TH) %>% dplyr::summarise(Average_Monthly = sum(Amount))

For_Profit <- cbind(monthly_Spent, monthly_Repayment)

For_Profit <- dplyr::rename(For_Profit, "SPENT" = "Average_Monthly...3", "REPAY" = "Average_Monthly...6")

For_Profit <- dplyr::rename(For_Profit, "YEAR" = "YEAR...1", "MONTH" = "MON_TH...2")
```

#### DROP USELESS COLUMN

```{r}
For_Profit$YEAR...4 <- NULL

For_Profit$MON_TH...5 <- NULL

For_Profit$PROFIT <- For_Profit$REPAY- For_Profit$SPENT

PROFIT_PLUS <- For_Profit[For_Profit$PROFIT > 0, ]

PROFIT_PLUS$Profit_AMOUNT <- (PROFIT_PLUS$PROFIT*2.9)/100

PROFIT_PLUS
```




####  f. What are the top 5 product types? 
  
  ```{r}
  TOP_5_PRODUCT <- spend %>% dplyr::group_by(Type) %>% dplyr::summarise(COU_NT = n()) %>% dplyr::arrange(desc(COU_NT))
 
 Top_5_Type  <- head(TOP_5_PRODUCT,5)

Top_5_Type
```  
  
  
####  g. Which city is having maximum spend? 
    
###### Customer Spent Data is Used For Solution 


```{r}
Maximum_Spend <- CUSTOMER_SPENT %>% dplyr::group_by(City) %>% dplyr::summarise(Total_Spend = 
                                                sum(Amount), Percentage = 
           round(sum(Amount)*100/sum(CUSTOMER_SPENT$Amount),2) ) %>% dplyr::arrange(desc(Total_Spend))
           
Maximum_Spend
```    
    
#### h. Which age group is spending more money?  (Age Group 18-36,36-54,54-72,72+)

  ```{r}
  
  CUSTOMER_SPENT$AGE_GROUP <-   ifelse(CUSTOMER_SPENT$Age <36, "YOUNG",
         ifelse(CUSTOMER_SPENT$Age <54, "MID_AGE", 
                ifelse(CUSTOMER_SPENT$Age <72, "MATURE", "OLD")))
                

  MOST_SPENT <- CUSTOMER_SPENT %>% dplyr::group_by(AGE_GROUP) %>% dplyr::summarise(Total_Spent = 
                              sum(Amount), Percentage = 
        round(sum(Amount)*100/sum(CUSTOMER_SPENT$Amount),2) ) %>% dplyr::arrange(desc(Percentage))

  
  MOST_SPENT
```  
  
####  i. Who are the top 10 customers in terms of repayment?
  
  ```{r}  
    Top_Customers <- CUSTOMER_Repayment %>% dplyr::group_by(Customer) %>% dplyr::summarise(Total_Repayment = 
                                                         sum(Amount)) %>% dplyr::arrange(desc(Total_Repayment))

  Top_10_Customers <- head(Top_Customers,10)

  Top_10_Customers
  
```


#### 3. Calculate the city wise spend on each product on yearly basis. Also include a 
####  graphical representation for the same. 

```{r}
YEARLY_CITY_PRODUCT_SPEND <-  CUSTOMER_SPENT %>% dplyr::group_by(YEAR,City,Product) %>%  dplyr::summarise(Total_Spend = sum(Amount))

YEARLY_CITY_PRODUCT_SPEND


ggplot2::ggplot(data = YEARLY_CITY_PRODUCT_SPEND) + aes(x= City, y = Total_Spend, fill = Product ) +
  geom_bar(stat = "identity", position = "dodge") + facet_grid(.~YEAR)
```


#### 4. Create graphs for 

####  a. Monthly comparison of total spends, city wise 

```{r}
CITY_WISE_spend <- CUSTOMER_SPENT %>% dplyr::group_by(City,MON_TH) %>% dplyr::summarise(TOTAL_SPEND =sum(Amount))

CITY_WISE_spend

ggplot2::ggplot(data = CITY_WISE_spend) + aes(x= City, y = TOTAL_SPEND, fill = MON_TH ) +
  geom_bar(stat = "identity", position = "dodge") 

```


####  b. Comparison of yearly spend on air tickets 

```{r}
Air_Ticket_Data<-    CUSTOMER_SPENT[CUSTOMER_SPENT$Type == "AIR TICKET",]

rownames(Air_Ticket_Data) <- NULL

YEARLY_AIR_TICKET <- Air_Ticket_Data %>% dplyr::group_by(YEAR) %>% dplyr::summarise(TOTAL_SPEND = sum(Amount))

ggplot2::ggplot(data = YEARLY_AIR_TICKET) + aes(x= YEAR, y = TOTAL_SPEND ) +
  geom_bar(stat = "identity", position = "dodge")
```



####  c. Comparison of monthly spend for each product (look for any seasonality that exists in terms of spend) 

```{r}
MONTHLY_SPEND <- CUSTOMER_SPENT %>% dplyr::group_by(MON_TH,Product) %>% dplyr::summarise(ToTAL_SPEND =sum(Amount))

ggplot2::ggplot(data = MONTHLY_SPEND) + aes(x= MON_TH, y = ToTAL_SPEND, fill = Product ) +
  geom_bar(stat = "identity", position = "dodge")

```

####   Spend is Decreasing in last Months as Compared to Starting Months


#### 5. Write user defined R function to perform the following analysis: 
#### You need to find top 10 customers for each city in terms of their repayment 
#### amount by different products and by different time periods i.e. year or 
#### month. The user should be able to specify the product 
#### (Gold/Silver/Platinum) and time period (yearly or monthly) and the function 
#### should automatically take these inputs while identifying the top 10 
#### customers.


```{r}

UDF_TOP10 <- function(DA_TA,YE_AR,Prod) { 
P_DATA =   DA_TA[(DA_TA$YEAR == YE_AR) & (DA_TA$Product == Prod),]
  require(dplyr)
 Pre_Result = P_DATA %>% dplyr::group_by(Customer) %>% dplyr::summarise(TOTALS_PEND = sum(Amount)) %>% dplyr::arrange(desc(TOTALS_PEND))
  Result = head(Pre_Result,10)
  print(Result) 
  
  }
```

####USe Character Data For Product ( Eg - "Gold", "Silver", "Platinum")

```{r}
UDF_TOP10(CUSTOMER_Repayment, 2004,"Gold")

UDF_TOP10(CUSTOMER_Repayment, 2004, "Silver")

UDF_TOP10(CUSTOMER_Repayment, 2004, "Platinum")
```
